---
title: ""
format: gfm
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%",
  eval = FALSE
)
```

## Getting started

`auditr` is a cross-platform (Windows and Linux) R package that provides R6 methods for auditing two releases of <a href="https://github.com/statcan/stcopenmpp" target="_blank">stcopenmpp</a>. The methods in this package allow users to download and extract two releases of `stcopenmpp`, clone and checkout a model from any point in its history, compile the model asynchronously in both releases, run the model asynchronously in both releases and generate an audit report in Quarto (`.html`). 

`auditr` interacts with model `.exe` files directly and relies on SQL queries to interact with model `.sqlite` files. This design eliminates the need for the OpenM++ web service and, consequently, reduces time significantly when doing model runs. `auditr` also cleans up model databases immediately after model runs and audits to avoid any unexpected incursions on storage capacity in the case of models with large and/or numerous output tables.

### Loading auditr

```{r, eval = FALSE}
# Set working directory
setwd("path/to/auditr")

# Load auditr
devtools::load_all()
```

### Using auditr

```{r, eval = FALSE}
# Initialize auditr R6 class
audit <- auditr$new(
  releases = c(
    "https://github.com/openmpp/main/releases/download/v1.17.9/openmpp_win_20250601.zip",
    "https://github.com/openmpp/main/releases/download/v1.17.10/openmpp_win_20250923.zip"
  ),
  labels = c(
    "OpenM++ v1.17.9",
    "OpenM++ v1.17.10"
  ),
  sln = "RiskPaths-ompp.sln",
  mode = "release",
  bit = 64,
  git_url = "https://github.com/openmpp/main.git",
  git_commit = "v1.17.9",
  vs_cmd = "c:/program files/microsoft visual studio/18/professional/common7/tools/vsdevcmd.bat",
  platform_toolset = "v145"
)

# Download and extract releases
audit$load_releases()

# Download model
audit$load_model()

# Compile model in both releases asynchronously
audit$build_models()

# Get list of model's non-hidden output tables
audit$load_output_tables()

# Initiate model runs and audit output tables in both releases asynchronously
audit$run_models(
  cases = 1e6,
  threads = 4,
  sub_samples = 4,
  tables_per_run = 5
)

# Generate Quarto report
audit$load_report()
```

#### Audit report

Download the report in `.html`: [inst/html/demo-auditr-report.html](inst/html/demo-auditr-report.html?inline=false)

#### Audit meta

```{r, eval = FALSE}
# View audit meta
audit$results$audit
```

```{r, eval = TRUE, echo = FALSE}
readRDS("inst/rds/demo-audit.rds") |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::everything(),
      .fns = ~ as.character(.x)
    ),
    dplyr::across(
      .cols = dplyr::everything(),
      .fns = ~ ifelse(
        test = nchar(.x) > 40,
        yes = stringr::str_trunc(
          string = .x,
          width = 40,
          side = "center"
        ),
        no = .x
      )
    )
  ) |> 
  print(n = Inf, width = Inf)
```

#### Model run meta

```{r, eval = FALSE}
# View model run meta
audit$results$model_runs
```

```{r, eval = TRUE, echo = FALSE}
readRDS("inst/rds/demo-model-runs.rds") |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::everything(),
      .fns = ~ as.character(.x)
    ),
    dplyr::across(
      .cols = dplyr::everything(),
      .fns = ~ ifelse(
        test = nchar(.x) > 30,
        yes = stringr::str_trunc(
          string = .x,
          width = 30,
          side = "center"
        ),
        no = .x
      )
    )
  ) |> 
  print(n = Inf, width = Inf)
```

#### Output tables

```{r, eval = FALSE}
# View list of non-hidden output tables
audit$results$output_tables
```

```{r, eval = TRUE, echo = FALSE}
readRDS("inst/rds/demo-output-tables.rds")  |>
  dplyr::mutate(
    dplyr::across(
      .cols = dplyr::everything(),
      .fns = ~ as.character(.x)
    ),
    dplyr::across(
      .cols = dplyr::everything(),
      .fns = ~ ifelse(
        test = nchar(.x) > 40,
        yes = stringr::str_trunc(
          string = .x,
          width = 40,
          side = "center"
        ),
        no = .x
      )
    )
  ) |> 
  print(n = Inf, width = Inf)
```

